Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-04-20 sources/bmc_template_submission/bmc_article.tex
MK edits page 6

Physcraper is a tool that builds upon previous knowledge stored in published
alignments, with the main goal to extend our knowledge of phylogenetic relationships
across the tree of life.

@@

We encourage users to look at this file, and potentially modify their sequence length cutoff parameters based on the excluded sequences.
The default relative sequence length thresholds are arbitrary, but we hope that by making the process of locating homologous sequences online reproducible, and tracking what cutoffs are used, we make it easier for researchers to delve into the effect that different choices have on their inferences.
This is in contrast to ``manual" searches for taxa, where similarly arbitrary cutoffs are applied, but are difficult to trace.
As many studies have shown \cite{huang_what_2009} the effect of missing data can be enigmatic, and interact with the true phylogenetic relationships for the data set at hand.
There is not currently strong support in the literature for any cutoffs, and rather than prescribe specific approaches, we encourage users to explore the effects of different choices on inference.

@@

Most of the default thresholds parameter values and software choices in the Physcraper pipeline are arbitrary.
We hope that by making the process of locating homologous sequences online reproducible,
and tracking what cutoffs are used, we make it easier for researchers to delve into the effect that different choices have on their inferences.
In addition, by providing the output files at each step of the analysis,
it is straightforward to assess how changing parameter and software choices do or do not drive differences in phylogenetic inference.
By gathering the sequences, and making the unaligned files easily available to users, researchers can compare if applying any alternate alignment tool of their choice affects inferences.
Once sequences are aligned, they can apply and compare inferences from any phylogenetic software.

>>>>

Physcraper is a tool that builds upon previous knowledge stored in published
alignments and phylogenies, taking advantage of OpenTree's services to facilitate comparison
of phylogenies, with the main goal of extending our knowledge of phylogenetic relationships
across the tree of life.

@@

We encourage users to look at the output files containing information about the
filtered sequences, and potentially modify configuration parameters such as the
sequence length cutoff parameter, based on the filtered sequences.
Default filtering parameters are arbitrary, but we hope that by making the process
of locating homologous sequences online reproducible, and tracking what filters
are used, we make it easier for researchers to delve into the effect that different
choices have on their inferences.
This is in contrast to ``manual" searches for taxa, where similarly arbitrary filters
are applied, but are difficult to trace.
As many studies have shown \cite{huang_what_2009} the effect of missing data can
be enigmatic, and interact with the true phylogenetic relationships for the data
set at hand.
There is not currently strong support in the literature for any particular cutoffs
value, and rather than prescribe specific approaches, we encourage users to explore
the effects of different choices on their phylogenetic inferences.
In addition, by providing the output files at each step of the analysis,
it is straightforward to assess how changing parameter and software choices do or
do not drive differences in phylogenetic inference.
By gathering the sequences, and making the unaligned files easily available to users,
researchers can compare if applying any alternate alignment tool of their choice
affects inferences.
Once sequences are aligned, they can apply and compare inferences from any phylogenetic
software.

@@
